\textbf{Computational Fuzzy Extractors}

### 2013-05-16 CompFuzzExt.tex
working on the intro

%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  The resulting secret key may be too short to be useful if the entropy loss is too high.  Traditionally, fuzzy extractors are defined as information-theoretic objects.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.

\bnote{This language is pretty clunky. Revise.}
The main novel tool in constructing fuzzy extractors is the secure sketch.  The secure sketch produces a public value $s$ that allows recovery of $w$ from any close value $w'$.  The security requirement is that $w$ has high min-entropy conditioned on $s$.  The key $r$ is formed by applying a randomness extractor~\cite{nisan1993randomness} to $w$.
%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application. When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high. 
The minimum entropy loss for secure sketches has been quantified in past work.  Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}, 
%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
the entropy loss of a secure sketch that can reconcile $t$ errors
 %with high probability 
 is bounded by the redundancy of
the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  Constructions of fuzzy extractors that use a secure sketch inherit this bound.
%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).

\paragraph {Our Contributions}
To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with a secrecy requirement that is computational rather than information-theoretic.  Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.

On the negative side, we show that the paradigm of secure sketch and extraction from~\cite{DBLP:journals/siamcomp/DodisORS08} is unlikely to be fruitful.  We show that some entropy loss is necessary for secure sketches.
The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.  We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.  
%Furthermore, we have (asymptotic)~constructions that meet these bounds.

@@

Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.  To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.

@@

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.  We consider two different notions for computational entropy, and for both of them show that we can do essentially as well information-theoretically as computationally.

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.  The code-offset sketch instantiated with a random linear code~(in the Hamming metric)  achieve min-entropys $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs\lnote{this point is confusing -- it's not the random linear codes, it's some construction applied to them in order to get a sketch -- we should cite appropriately and explain more clearly here and in 3.2}, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.  Do we prefer $n\log Z$?} \lnote{I think your change is fine}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

\begin{theorem}
\label{thm:imp of unp entropy}
Let $Z$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
\end{theorem}
In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.  Essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the code-offset construction\lnote{cite here, and is it the randomized construction or the deterministic one that we should use here?} applied to the best possible codes (e.g., random codes\lnote{cite performance of codes?}).  Thus, unpredictability-entropy secure sketches cannot improve on the best possible information-theoretic entropy loss (at least for uniform inputs).  However, because the best possible codes may not have efficient decoding, it is conceivable that unpredictability entropy secure sketch could achieve lower entropy loss than is possible with efficient information-theoretic sketches.

This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  \lnote{I find the previous three sentences more confusing than helpful; do we really need them?  should we reword or remove?} %Our bound is a result of the Hamming bound for the space.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))<\epsilon.
\]  
where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. Let $X_y$ denote the random variable $X|Y=y$.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $w\in\mathcal{M}, z \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $w'\leftarrow \neigh(w, t')$.
\subitem If $\rec(w', z) \neq  w$ output $0$.
\item Output $1$.
\end{enumerate}
 By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((W, \sketch(W)), (X, Y))<\epsilon$, we know $\Pr[D(X, Y) = 1]>1-\epsilon-t\delta$.  By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]> 1- 2(\epsilon + t\delta)$.

Because $\Hav(X | Y)\geq k$, we know that $\expe_{y\leftarrow Y} \max_x \Pr[X_y=x]\leq 2^k$.  Applying Markov's inequality to the random variable $\max_x \Pr[X_y=x]$, there exists a set $S'_Y$ such that $\Pr[y\in S'_Y]> 1/2$, and for all $y\in S'_Y$, $\Hoo(X_y)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_x \Pr[X_y=x]$ is positive).  Fix one value $y \in S_Y\cap S'_Y$ (which exists because the sum of probabilities of $S_Y$ and $S'_Y$ is greater than 1).  
Thus, for all such that $t', 1\leq t'\leq t$, 
\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \sample(x, t') \wedge \rec(x',z) = x]> 1-2(\epsilon+t\delta).\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $X_y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,y)$ and $2^{k-1}$ points.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}

\thref{thm:imp of unp entropy} follows by noting that $Z^n$ can be sampled in time $n\log |Z|$ and neighborhood sampled in time $n\log |Z|$.
\subsection{Proof of \thref{thm:imp of unp entropy}}
\label{sec:proof of imp unp entropy}
Instead of proving \thref{thm:imp of unp entropy}, we will prove a stronger result based on a weaker form of entropy.  This relaxed definition allows both the variable and the condition to be replaced.  This is analogous to the relaxed HILL entropy~(see \defref{def:relaxed hill}).%Gentry and Wichs utilize an analogous relaxation for HILL entropy in~\cite[Lemma 3.1]{gentry2011separating}~(we provide a formulation of this notion in \defref{def:relaxed hill}).

\begin{definition}
\label{def:relaxed unp entropy}
For a distribution $(W, S)$, we say that $W$ has \emph{relaxed unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unprlx}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a joint distribution $X, Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, Y))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size at most $s_{sec}$,
\[
\Pr[\mathcal{I}(Y) = X ] \leq 2^{-k}
.\]
\end{definition}

We will prove the result for a metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.  We now define this second condition:
\begin{definition}
A metric space space $(\mathcal{M}, \dis)$ is $s_{sam}$-\emph{efficiently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that outputs a uniformly random point in $\mathcal{M}$.
\end{definition}

\begin{theorem}
Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.  Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is fixed~(this quantity is denoted by $B_t(\cdot)$).  Let $(\sketch, \rec)$ be a relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.
\end{theorem}
\begin{proof}
Let $\mathcal{M}, \dis$ be a $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable metric space~(by procedures $\sample$ and $\neigh$ respectively).  
Let $W$ be a distribution over $\mathcal{M}$ and let $(\sketch, \rec)$ be an relaxed unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$ where $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$.  Let $X, Y$ be a joint distribution such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.  It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq 2^{\tilde{m}}$ where $\tilde{m} = \log |\mathcal{M}| - \log |B_t(\cdot)| - \log(1-\epsilon -t\delta)$.

Let $B_t(x)$ denote the random variable of a random neighbor of distance at most $t$ from $x$.  Recall, the algorithm $\neigh$ outputs neighbors at a fixed distance, the random variable $B_t(x)$ may not be efficiently computable, we use it as a random variable.
We begin by showing that \rec must recover points of $X$.  
\begin{claim}
\label{clm:y is recoverable}
\begin{align*}
\Pr[\rec(B_t(X), Y) = X]&=\\
\Pr[(x, y)\leftarrow (X, Y) \wedge x'\leftarrow B_t(x) \wedge \rec(x', y) = x] &\geq 1-\epsilon -t\delta.
\end{align*}
\end{claim}
\begin{proof}
Suppose that $\Pr[\rec(B_t(X), Y) = X]<1-\epsilon -t\delta$.  We construct the following $D\in\mathcal{D}_{s_{sec}}$:
\begin{itemize}
\item Input $w\in \mathcal{M}, s\in\zo^*$.
\item For all $1\leq t'\leq t$: 
\subitem  $w'\leftarrow \neigh(w, t')$.
\subitem If $\rec(w', z) \neq  w$ output $0$.
\item Output $1$.
\end{itemize}
First note that $|D| = t( |\rec|+ s_{neigh} )$.  Since $(\rec, \sketch)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.  If $\Pr[\rec(B_t(X), Y) = X] < 1-\epsilon -t\delta$ there must exist some $1\leq t'\leq t$ where this is true.  Then 
\begin{align*}
\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(X, Y)=1] &\geq\\
(1-t\delta) - \Pr[\rec(\neigh(X, t'), Y) = X] &> (1-t\delta)-(1-t\delta - \epsilon)>\epsilon.
\end{align*}
This is a contradiction and the statement of the claim follows.
\end{proof}
We now consider the experiment $(x, y)\leftarrow (X, Y), x'\leftarrow B_t(x)$ and define the quantity $P_{x' , y,x} = \Pr[\rec(x', y) =x]$.  \clref{clm:y is recoverable} says that 
\[
 \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in \mathcal{M}} \Pr[B_t(x) =x' | X = x] P_{x',  y,x} \geq 1-\epsilon - t\delta.
\]
We note that for any particular $x, x'$ such that $\dis(x, x')\leq t, \Pr[B_t(x) = x' | X=x] = 1/|B_t(\cdot)|$ and if $\dis(x, x')>t, \Pr[B_t(x) = x' | X=x] = 0$.  Thus, for all $x, x', \Pr[B_t(x) = x' | X=x] \leq 1/|B_t(\cdot)|$.
Now define $\mathcal{I}\in\mathcal{D}_{s_{sec}}$ as follows:
\begin{itemize}
\item Input $y\in\zo^*$.
\item Sample $x\leftarrow \sample(\cdot)$.
\item Output $\rec(x, s)$.
\end{itemize}
Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$.  Let $X'$ the random variable corresponding to the sample $x$ taken by $\decode_t$.
We now show that $\mathcal{I}$ predicts $X$:
\begin{align*}
2^{\tilde{m}}& = \Pr[\mathcal{I}(Y) = x] \\
&= \Pr[(x, y)\leftarrow (X, Y)] \Pr[\mathcal{I}(y) = x]\\
&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[X' = x' ]\Pr[\mathcal{I}(y) = x | X = x']\\
&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[X' = x' ] P_{x', y, x}\\
&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \frac{\Pr[X' = x']}{\Pr[B_t(x) = x' | X = x]}\Pr[B_t(x) = x' | X=x ] P_{x', y, x}\\
&\geq \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \frac{1/|\mathcal{M}|}{1/|B_t(\cdot)|} \Pr[B_t(x) = x' | X=x ] P_{x', y, x}\\
&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[B_t(x) = x' | X=x ] P_{x', y, x}\\
&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|}(1-\epsilon - t\delta)
\end{align*}
Finally converting to entropy, one has $\tilde{m}\leq \log |\mathcal{M}|-\log |B_t(\cdot)| - \log (1-\epsilon -t \delta)$.
\end{proof}

>>>>

%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful Traditionally, fuzzy extractors are defined as information-theoretic objects.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.

We ask whether it is possible to obtain longer keys by considering
computational, rather than information theoretic, security.

\paragraph {Our Contributions}
We first study whether improvements are possible by relaxing the definition of the main building block of fuzzy extractors, called \emph{secure sketch}.  A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$ (The key $r$ is formed by the fuzzy extractor by applying a randomness extractor~\cite{nisan1993randomness} to $w$.)  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.

The most natural relaxation of the secrecy requirement is to require HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99}~(namely, that the distribution of $w$ conditioned on $s$ be \emph{indistinguishable} from a high-min-entropy distribution).  Under this definition, using the paradigm for constructing fuzzy extractors from~\cite{DBLP:journals/siamcomp/DodisORS08} would yield a pseudorandom key.  We prove in Theorem~\ref{thm:impSketchArbitraryW} that the entropy loss of such secure sketches is subject to the same coding bounds as the ones that constrain information-theoretic secure sketches.  
%Furthermore, we have (asymptotic)~constructions that meet these bounds.

@@

Both of these impossibility results arise because a secure sketch functions like a decoder of an error-correcting code.  To avoid these impossibility results, we give up on building secure sketches and focus directly on the entropy loss in fuzzy extractors.  
\lnote{stopped here}

%Secret entropy of convenient sources is often at a premium; a goal of secure sketch constructions is to minimize the entropy loss, increasing the security of the resulting application. When used in a fuzzy extractor, the resulting secret key may be too short to be useful if the entropy loss is too high. 
The minimum entropy loss for secure sketches has been quantified in past work.  Even if $\rep$ is allowed to produce an incorrect value with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}, 
%Even if we don't require perfect correctness (i.e., allow $\rep$ to err with small probability~\cite[Section 8]{DBLP:journals/siamcomp/DodisORS08}), 
the entropy loss of a secure sketch that can reconcile $t$ errors
 %with high probability 
 is bounded by the redundancy of
the best code that can correct $t$ random errors with high probability~\cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  Constructions of fuzzy extractors that use a secure sketch inherit this bound.
%(the argument is the same as in \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08}\lnote{probably we should double-check that this is correct}).

To see if entropy loss in fuzzy extractors can be improved, we explore fuzzy extractors and secure sketches with a secrecy requirement that is computational rather than information-theoretic.  Our goal is to decrease the entropy loss in a fuzzy extractor by allowing the key $r$ to be pseudorandom conditioned on $p$.

On the negative side, we show that the paradigm of secure sketch and extraction from~\cite{DBLP:journals/siamcomp/DodisORS08} is unlikely to be fruitful.  We show that some entropy loss is necessary for secure sketches.

@@

%=============================================================
\section{Impossibility of Computational Secure Sketches}
\label{sec:defCompFuzzyExtractors}
In this section, we consider whether it is possible in build a secure sketch that retains significantly more computational than information-theoretic entropy.  We consider two different notions for computational entropy, and for both of them show that we can do essentially as well information-theoretically as computationally. \lnote{too strong?} Thus, it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on high-entropy sources.

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In particular, for the case of the Hamming metric and inputs that have full entropy, our results are as follows.  In  \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$. Dodis et al. \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  construct sketches with essentially the same information-theoretic security\footnote{The security in  \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08}  is expressed in terms of entropy of the error rate; recall that $\log B_t(\cdot)\approx H_q(t/n)$, where $n$ is the number of symbols, $q$ is the alphabet size, and $H_q$ is the $q$-ary entropy function.} .

In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

\begin{theorem}
\label{thm:imp of unp entropy}
Let $Z$ be an alphabet $(\sketch, \rec)$ be an unpredictability-entropy $(Z^n, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
\end{theorem}
In particular, if the input is uniform, the entropy loss is about $\log |B_t(\cdot)|$.  As mentioned at the beginning of~\secref{sec:defCompFuzzyExtractors}, essentially the same entropy loss can be achieved with information-theoretic secure sketches, by using the randomized code-offset construction. However, it is conceivable that unpredictability entropy secure sketches could achieve lower entropy loss with greater efficiency for some parameter settings.

%This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  \lnote{I find the previous three sentences more confusing than helpful; do we really need them?  should we reword or remove?} %Our bound is a result of the Hamming bound for the space.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(X, Y)$ be a joint distribution such that $\Hav(X | Y)\geq k$ and
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\le \epsilon\, ,
\]  
where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(X, Y)$ must exist by the definition of conditional HILL entropy. Let $X_y$ denote the random variable $X|Y=y$.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $w\in\mathcal{M}, z \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $w'\leftarrow \neigh(w, t')$.
\subitem If $\rec(w', z) \neq  w$ output $0$.
\item Output $1$.
\end{enumerate}
 By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((W, \sketch(W)), (X, Y))\le \epsilon$, we know $\Pr[D(X, Y) = 1]\ge 1-\epsilon-t\delta$.  By Markov's inequality,  there exists a set $S_Y$ such that $\Pr[Y\in S_Y]\ge 1/2$ and for all $y\in S_Y$, $\Pr[ D(X_y, y) =1]\ge 1- 2(\epsilon + t\delta)$.

Because $\Hav(X | Y)\geq k$, we know that $\expe_{y\leftarrow Y} \max_x \Pr[X_y=x]\leq 2^k$.  Applying Markov's inequality to the random variable $\max_x \Pr[X_y=x]$, there exists a set $S'_Y$ such that $\Pr[y\in S'_Y]> 1/2$, and for all $y\in S'_Y$, $\Hoo(X_y)\ge k-1$ (we can use the strict version of Markov's inequality here, because the random variable $\max_x \Pr[X_y=x]$ is positive).  Fix one value $y \in S_Y\cap S'_Y$ (which exists because the sum of probabilities of $S_Y$ and $S'_Y$ is greater than 1).  
Thus, for all such that $t', 1\leq t'\leq t$, 
\[ \Pr_{x\leftarrow X_y}[x'\leftarrow \sample(x, t') \wedge \rec(x',z) = x]\ge  1-2(\epsilon+t\delta).\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $X_y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,y)$ and $2^{k-1}$ points.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}

\thref{thm:imp of unp entropy} follows by noting that $Z^n$ can be sampled in time $n\log |Z|$ and neighborhood sampled in time $n\log |Z|$.
\subsection{Proof of \thref{thm:imp of unp entropy}}
\label{sec:proof of imp unp entropy}
Instead of proving the result just for Hamming metric over $Z^n$, we will prove the result for any metric space that is both neighborhood samplable~(\defref{def:neighborhood samplable}) and where picking a random point in the space is easy.  We now define this second condition:
\begin{definition}
A metric space space $(\mathcal{M}, \dis)$ is $s_{sam}$-\emph{efficiently-samplable} if there exists a randomized circuit $\sample$ of size $s_{sam}$ that outputs a uniformly random point in $\mathcal{M}$.
\end{definition}

\begin{theorem}
Let $W$ be a distribution over a metric space $(\mathcal{M}, \dis)$ that is $s_{sam}$ samplable and $(s_{neigh}, t)$ neighborhood samplable.  Furthermore, assume that the number of points within distance $t$ in $\mathcal{M}$ is at least $B_t(\cdot)$.  Let $(\sketch, \rec)$ be an unpredictability-entropy $(\mathcal{M}, \Hoo(W), \tilde{m}, t)$ secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq \max\{ t(|\rec| +s_{neigh}), |\rec| + s_{sam}\}$, then $\tilde{m}\leq \log |\mathcal{M}| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
\end{theorem}
\begin{proof}
Let $(X, Y)$ be two random variables such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (X, Y))\leq \epsilon$.  It suffices to show that $\exists \mathcal{I}$ of size $s_{sec}$ such that $\Pr[\mathcal{I}(Y) = X]\geq |\mathcal{M}| (1-\epsilon -t\delta) / |B_t(\cdot)|$.

Let $B_t(x)$ denote the random variable representing a random neighbor of distance at most $t$ from $x$ (note that $B_t$ may not be efficiently samplable, because we are assuming only that a neighbor a fixed distance is efficiently samplable).
We begin by showing that \rec must recover points of $X$.  
\begin{claim}
\label{clm:y is recoverable}
\begin{align*}
\Pr[\rec(B_t(X), Y) = X]&=\\
\Pr[(x, y)\leftarrow (X, Y) \wedge x'\leftarrow B_t(x) \wedge \rec(x', y) = x] &\geq 1-\epsilon -t\delta.
\end{align*}
\end{claim}
\begin{proof}
Suppose that $\Pr[\rec(B_t(X), Y) = X]<1-\epsilon -t\delta$.  We construct the following distinguisher $D\in\mathcal{D}_{s_{sec}}$ (the distinguisher design is slightly complicated by the fact that we don't know at which particular distance $t'$ the recover procedure is most likely to fail, so we have to try all distances):
\begin{itemize}
\item Input $w\in \mathcal{M}, s\in\zo^*$.
\item For all $1\leq t'\leq t$: 
\subitem  $w'\leftarrow \neigh(w, t')$.
\subitem If $\rec(w', z) \neq  w$ output $0$.
\item Output $1$.
\end{itemize}
First note that $|D| = t( |\rec|+ s_{neigh} )$.  Since $(\sketch, \rec)$ has error $\delta$ we know that $\forall w, w'\in \mathcal{M}$ where $\dis(w, w')\leq t$ \[ \Pr[s\leftarrow \sketch(w) \wedge \rec(w', s) =  w] \geq 1-\delta.\]  This implies that for all $1\leq t'\leq t$, $\Pr[\rec(\neigh(W, t'), \sketch(W) )= W)  ]\geq 1-\delta$ and thus $\Pr[D(W, \sketch(W)) = 1]\geq 1-t\delta$.  If $\Pr[\rec(B_t(X), Y) = X] < 1-\epsilon -t\delta$ there must exist at least one $1\leq t'\leq t$ for which $\Pr[\rec(\neigh(X, t'), Y) = X] < 1-\epsilon -t\delta$.  Then 
\begin{align*}
\Pr[D(W, \sketch(W)) = 1]  - \Pr[D(X, Y)=1] &\geq\\
(1-t\delta) - \Pr[\rec(\neigh(X, t'), Y) = X] &> (1-t\delta)-(1-t\delta - \epsilon)>\epsilon.
\end{align*}
This is a contradiction and the statement of the claim follows.
\end{proof}

Now define $\mathcal{I}$ as follows:
\begin{itemize}
\item Input $y\in\zo^*$.
\item Sample $x'\leftarrow \sample$.
\item Output $\rec(x', y)$.
\end{itemize}
Note that $|\mathcal{I}| =  |\rec|+ s_{sam}$. 
We now show that $\mathcal{I}$ predicts $X$:
\begin{align*}
\Pr[\mathcal{I}(Y) = X] & = \\
&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \Pr[\mathcal{I}(y) = x]\\
&= \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\in\mathcal{M}} \Pr[\sample = x' ] \Pr[\rec(x', y) =x]\\
&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x' \mathrm{ s. t. } \dis(x', x)\le t} \Pr[\sample = x']\Pr[\rec(x', y) =x]\\
&\ge \sum_{x, y\in \mathcal{M}} \Pr[(x, y)\leftarrow (X, Y)] \sum_{x'\mathrm{ s. t. } \dis(x', x)\le t} \frac{|B_t(\cdot)|}{|\mathcal{M}|} \Pr[B_t(x) = x'] \Pr[\rec(x', y) =x]\\
&\geq \frac{|B_t(\cdot)|}{|\mathcal{M}|}(1-\epsilon - t\delta)
\end{align*}
(the last step follows by  \clref{clm:y is recoverable}).
\end{proof}
